\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{comment}
\pdfgentounicode=1

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{5pt}

% Style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-0.2cm}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom Commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{\href{#2}{#1}} $|$  \textbf{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% Resume
\begin{document}

%----------HEADING----------

\begin{tabularx}{\textwidth}{X r}
  \textbf{\LARGE Ashish Kushwaha} & \href{https://github.com/ashish-kus}{\textcolor{blue}{github.com/ashish-kus}} \\
  \textbf{Software Developer Engineer} & \href{mailto:ashish.kus2408@gmail.com}{\textcolor{blue}{ashish.kus2408@gmail.com}} \\
  Mobile: +91 7525874187 & \href{https://www.linkedin.com/in/ashish-kushwaha2408}{\textcolor{blue}{linkedin.com/in/ashish-kushwaha2408}} \\
\end{tabularx}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Gautam Buddha University}{Greater Noida, Uttar Pradesh}
    {B. Tech + M. Tech CSE in Software Engineering, CGPA: 8.5}{August 2020 -- Present}
  \resumeSubheading
    {Narayana IIT Academy, Raviryala}{Hydrabad, Telangana State}
    {Intermediate – Physics, Chemistry, Mathematics: 88\%}{March 2017 -- March 2019}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Software Development Engineer | Arial Labs}{June 2024 – April 2025}
    {California, Remote}{}
    \resumeItemListStart
      \resumeItem{Independently developed the company’s core Chrome extension using React.js, Tailwind CSS, and Manifest V3 with cross-browser support, following SDLC best practices.}
      \resumeItem{Integrated Claude API with backend services using AWS Lambda, DynamoDB, and S3 to enable serverless, scalable AI-powered functionality, while maintaining code via GitHub and ensuring cloud security awareness.}
      \resumeItem{Configured and managed AWS environments, deploying the MVP through automated CI/CD pipelines, and collaborated via Jira to resolve issues with strong troubleshooting and analytical skills.}
    \resumeItemListEnd

  \resumeSubheading
    {Internship Trainee | Samsung Innovation Campus}{June 2024 – Sept 2024}
    {Greater Noida, Offline}{}
    \resumeItemListStart
      \resumeItem{Developed and fine-tuned machine learning and AI models using Python, TensorFlow, and PyTorch.}
      \resumeItem{Applied AI techniques for data classification, prediction, and pattern recognition on large datasets.}
      \resumeItem{Performed ETL processes, exploratory data analysis (EDA), and created visual dashboards using Power BI and Excel.}
    \resumeItemListEnd

\begin{comment}
  \resumeSubheading
    {Web Developer Intern | SOMHH}{Nov 2023 – Jan 2024}
    {Delhi, Remote}{}
    \resumeItemListStart
      \resumeItem{Developed a static fundraising website using Svelte and Bootstrap, significantly enhancing digital presence and outreach.}
      \resumeItem{Integrated Razorpay and Stripe payment gateways, streamlining the donation process and improving user experience.}
    \resumeItemListEnd
\end{comment}

    \resumeSubheading
    {Web Developer Intern | Gautam Buddha University}{March 2023 – June 2023}
    {Greater Noida, in campus}{}
    \resumeItemListStart
      \resumeItem{Designed and developed a frontend of web app with MERN stack to manage and track job applicants for university positions.}
      \resumeItem{Collaborated with the Registrar’s Office to gather requirements and deliver features, optimizing the hiring process.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {HireLift}{https://chromewebstore.google.com/detail/hirelift/gchcmaknjamkfbcgbafcchcglpeagidi}{Chrome Extension APIs, WebSockets, AWS Lambda, S3, DynamoDB, and REST APIs.}{}
    \resumeItemListStart
      \resumeItem{AI-powered Chrome extension used by 10+ hiring managers across 60+ interviews to streamline technical evaluations.}
      \resumeItem{Integrates with Google Meet/MS Teams to analyze live captions and JD–CV uploads, generating real-time questions.}
      \resumeItem{Generates post-interview summaries with tech skills, JD alignment, and key candidate insights via the dashboard.}
    \resumeItemListEnd

\begin{comment}
  \resumeProjectHeading
  {Mtag Gen}{https://github.com/ashish-kus/SEO_metaTag_generater}{Meta Tag Generator $|$ HTML, CSS, JavaScript, Netlify}{}
  \resumeItemListStart
    \resumeItem{Developed an intuitive web app to preview and generate SEO meta tags (HTML, Open Graph, Twitter Cards) for websites.}
    \resumeItem{Allows users to fetch metadata from a URL or manually input values to create optimized tags in seconds.}
    \resumeItem{Deployed on Netlify and featured a clean UI/UX focused on simplicity, accessibility, and quick SEO validation.}
  \resumeItemListEnd
\end{comment}

\resumeProjectHeading
  {Pixelify}{https://pixelify.netlify.app/}{React, Tailwind CSS, Sanity.io, OAuth, Netlify, Git/GitHub}{}
    \resumeItemListStart
      \resumeItem{A full-stack Pinterest-style image sharing platform with dynamic pin uploads, user authentication, and real-time updates.}
      \resumeItem{Includes Masonry layout, category filtering, pin detail view with comments, and secure pin creation with upload previews.}
    \resumeItemListEnd


\begin{comment}
\resumeProjectHeading
  {Huegen – Systems Theme Generator}{https://github.com/ashish-kus/huegen}{ C++17, OpenCV, nlohmann/json, linux, CMake, Template Engine}{}
    \resumeItemListStart
      \resumeItem{A C++17 tool to extract dominant colors from images using K-means clustering and LAB-based perceptual filtering.}
      \resumeItem{Built a template engine to auto-generate multi-format theme files (HEX, RGB, HSL, etc.) for Waybar, Hyprland, and more.}
      \resumeItem{Designed a modular architecture with customizable templates and automation hooks for instant theme application.}
    \resumeItemListEnd


\resumeProjectHeading
{Waybar-Hotspot}{https://github.com/ashish-kus/waybar-hotspot}{ Bash, Zenity, create\_ap, QR}{}
  \resumeItemListStart
    \resumeItem{Waybar module for monitoring and managing Wi-Fi hotspot status with graphical prompts using Zenity.}
    \resumeItem{Supports custom configurations for create\_ap and QR code display in tooltips for easy access.}
  \resumeItemListEnd


  \resumeProjectHeading
  {Batfetch}{https://github.com/ashish-kus/batfetch}{Linux Battery Information Analyzer $|$ Shell, JSON, CLI, Makefile, AUR}{}
    \resumeItemListStart
      \resumeItem{Command-line tool inspired by \texttt{pfetch}, display detailed battery information in a clean format with optional JSON output.}
      \resumeItem{Supports multiple installation methods including AUR, manual install via Makefile, and Nix Flake.}
      \resumeItem{Open source project with 4 open, 4 closed and 2 closed, 1 open pull request. This is avalable on Arch user Repositories.}
    \resumeItemListEnd

\end{comment}
\resumeSubHeadingListEnd

\section{Technical Skills}
   \resumeItemListStart[label={}]
      \resumeItem{  \textbf{Programming Languages}: C++, C, Bash, JavaScript, Python, Lua, LaTeX, HTML, CSS. } 
       \resumeItem{ \textbf{Frameworks \& Libraries}: ReactJS, FXTUI, TailwindCSS, Chrome Extensions, YAML.}
       \resumeItem{\textbf{Databases}: MySQL, MongoDB. }
       \resumeItem{\textbf{Tools}: SEO, AWS, QEMU, Linux, Git, GitHub, github actions, Docker, nginx, Linux, S3, cloudWatch, Vagrant.}
       \resumeItem{ \textbf{Soft Skills}: Effective Communication, Problem-Solving, Leadership, Adaptability, Team Collaboration. }
  \resumeItemListEnd

%-----------COMMUNITY-----------
\section{Certification, Publication \& Achievements}
\resumeItemListStart
  \resumeItem{Published research paper titled “Adaptive Task-Based CPU Scaling for Efficient Power Allocation in Edge Computing” at CVR2025. The paper will be part of the Springer Book Series: Lecture Notes in Networks and Systems.}
  \resumeItem{Introduction to Linux (LFS101) by The Linux Foundation, covering core Linux systems and essential fundamentals.}
  \resumeItem{Earned the Hacktoberfest 2024 badge and published multiple packages on the Arch User Repository (AUR).}
  \resumeItem{Earned the Oracle Cloud Infrastructure Essentials badge, gaining hands-on experience with core OCI services and architecture.}
\resumeItemListEnd

\end{document}

